\textbf{ \Large{Decentralized, autonomous sensor fault detection using neural networks}}

### 2015-01-19 Paper/PaperJahrSchlich.tex
Kapitel Laboratory Experiments angefangen - teststruktur beschrieben.

\documentclass[12pt]{scrartcl}
\usepackage[ngerman, english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[color=yellow!15]{todonotes}
\usepackage{graphicx}
\usepackage[numbers, square]{natbib}

% used for line numbering
\usepackage{lineno}

@@

\baselineskip24pt

@@

\linenumbers % Schaltet Zeilennummerierung ein
%\modulolinenumbers[5] % nur jede 5. Zeile
\section*{Dictionary}

@@

\textbf{1. paragraph: neural networks general}

\todo[inline]{Die Vorteile von neuronalen Netzwerken müssen m.E. noch in der Einleitung heruasgearbeitet werden}

Artificial neural networks were developed, driven by the desire to enable computer systems to learn autonomously.
This development is based on the attempt to emulate the data processing mechanics of the human brain. %(and is therefore inherently interwoven with advances in neuroscience)
In an artificial neural network \emph{neurons} are grouped in different \emph{layers}, as depicted in figure~\ref{fig:neuralnetwork}. 
Each neuron sends data exclusively to neurons from neighbouring layers through weighted \emph{connections}.
For each neuron a \emph{propagation function} processes incoming data, in consideration of the connection weights, to the net input.
An \emph{activation function} then processes the net input to calculate the activation of the neuron, which subsequently determines its output. \cite{KrieselNN}

A neural network learns, most commonly, by adjusting its connection weights until it recreates the results of a desired transfer function with sufficient accuracy.
In our case...
\todo[inline]{Weiteres zur Gewichtsveränderung in der Lernphase später im Abschnitt}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/neuralnetworks.pdf}
    \caption{Schematic drawing of an artificial neural network with three layers}
    \label{fig:neuralnetwork}
\end{figure}
\todo[inline]{Grafik kann nacher noch an unser neuronales Netz angepasst werden}

@@

\textbf{1. paragraph: test setup}

\begin{itemize}
\item test structure, picture
\item sensor installation
\item type of excitation, acceleration is measured

\end{itemize}

@@

\section*{Discussion of the experimental results}

@@

>>>>

\documentclass[12pt,a4paper]{scrartcl}
\usepackage[ngerman, english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[color=yellow!15]{todonotes}
\usepackage{graphicx}
\usepackage[numbers, square]{natbib}

% used for line numbering
%\usepackage{lineno}

@@

\baselineskip32pt

@@

%\linenumbers % Schaltet Zeilennummerierung ein
%\modulolinenumbers[5] % nur jede 5. Zeile
\section*{Dictionary}

@@

Neural networks are implemented into the sensor nodes using SNIPE\footnote{}, a open source Java Library.
\begin{figure}[ht]
    \centering
    \includegraphics{figures/neuralnetwork.pdf}
    \caption{Schematic drawing of an artificial neural network with three layers}
    \label{fig:neuralnetwork}
\end{figure}
\todo[inline]{Grafik kann nacher noch an unser neuronales Netz angepasst werden}

@@

%\begin{itemize}
%\item test structure
%\item sensor installation
%\item type of excitation, acceleration is measured
%\end{itemize}

To validate the proposed approach, the SHM system was installed on a test structure in order to conduct laboratory experiments.
The test structure consists of four metal sheets with an area of 20~cm by 60~cm and 4~mm of thickness.
Those metal sheets are mounted on threaded rods with a vertical clearance of approximately 40~cm.
At the bottom, the threaded rods are fixed into a block of solid wood with an area of 40~cm by 60~cm and a height of 50~cm.
The SHM system is installed onto the test structure by strapping a SunSPOT to each of the metal sheets.
The finished laboratory setup is shown in figure~\ref{fig:teststructure}.
\todo{Bild ersetzen durch ein Bild mit den fertig installierten SPOTS}
The structure is excited by pulling one of the metal sheets a few centimeters to the side and releasing it.
This method of excitation ensures, that the structure vibrates in its Eigenfrequency with little interferences.

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.3]{figures/teststructure.jpg}
    \caption{Picture of the laboratory setup}
    \label{fig:teststructure}
\end{figure}

@@

%\section*{Discussion of the experimental results}

@@

Everything went better than expected!
%----------------------------------------------------------------------------------------
